\LARGE \bf Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft

### 2016-03-24 paper.tex
added nasa model

The third model used to try to represent the aerodynamics of each rotor blade was

>>>>

The third model used to represent the aerodynamics and thrust of each rotor blade was from \cite{chen1979simplified}, a NASA model used in helicopter simulations several years ago. Instead of trying to implement blade element theory across the blade, this new model is able to approximate the thrust and torque required for the rotor given numerous variables. Instead of only varying rotor radius and fuel consumption rate, like last homework's model, this model attempts to optimize given rotor radius, fuel consumption rate, number of blade per rotor, number of rotors, rotor speed, and rotor pitch. The thrust, T, is given by equation \ref{thrust} and the torque, Q, is represented by equations \ref{torque} and \ref{torquecoeff}.

\begin{multline}
T = \frac{N}{2} \rho a c R (\omega R)^2 (.5 (1-\epsilon^2) \lambda \\
 + \theta_0 (\frac{1}{3} + \frac{\mu^2}{2} (1-\epsilon)) + \theta_t (.25+\frac{\mu^2}{2} (1-\epsilon^2))\\
- \frac{\mu}{2} (1-\epsilon^2) (B_{lc}-K_l b_l) - a_0 (\frac{1}{3} +\frac{\mu^2}{2} (1-\epsilon)) K_l \\
+ a_l (\frac{\mu}{2} \epsilon (1-\epsilon)) - \frac{\dot{a_0}}{\omega} (\frac{1}{3} -\frac{\epsilon}{2}) + \frac{\dot{b_l}}{\omega} (\frac{\mu}{4} (1-\epsilon)^2) \\
+ \frac{\mu}{4} (1-\epsilon^2) (\frac{p}{\omega cos(\beta_w)} + \frac{q}{\omega sin(\beta_w))} ) - N M_\beta \ddot{a_0}
\label{thrust}
\end{multline}
and
\begin{equation}
Q = N/2 \rho a c R^2 (\omega R)^2 (Q_{coeff})
\label{torque}
\end{equation}
where
\begin{multline}
Q_{coeff} = \delta/(4 a) (1 + (1-\epsilon^2) \mu^2) \\
 - (\theta_0 - K_l a_0)(\lambda/3+(\epsilon/3-.25) \dot{a_0}/\omega + \mu/6 \dot{b_l}/\omega\\  
- \mu \epsilon/4 (\dot{b_l}/\omega-a_l) + \mu/6 (p/\omega cos(\beta_w) +q/\omega sin(\beta_w))) \\
- (A_{lc}-K_l a_l) ((.125-\epsilon/6) (\dot{a_l}/\omega+b_l)-\mu/6 a_0 \\
+b_l/16 (1-\epsilon^2) \mu^2+1/8 (-p/\omega sin(\beta_w)+q/\omega cos(\beta_w)))\\ 
- (B_lc-K_l b_l) ((.125-\epsilon/6) (\dot{b_l}/\omega-a_l)\\
+(\epsilon/4-1/6) \mu \dot{a_0}/\omega+.5 (1-\epsilon^2) (\mu \lambda/2+a_l/8 \mu^2)\\ 
+ 1/8 (p/\omega cos(\beta_w)+q/\omega sin(\beta_w))) - \theta_t (\lambda/4\\ 
+ (\epsilon/4-1/5) \dot{a_0}/\omega+\mu/8 (\dot{b_l}/\omega)-\epsilon \mu/6 (\dot{b_l}/\omega-a_l))\\  
- .5 (1-\epsilon^2) (\lambda^2+\lambda \mu a_l+2 \lambda \epsilon \dot{a_0}/\omega\\  
+\mu \epsilon (a_l \dot{a_0}/\omega+a_0 (\dot{a_l}/\omega+b_l))\\  
+ \mu^2 (a_0^2/2+3/8 a_l^2+1/8 b_l^2)) + \mu/3 (a_l (\dot{a_0}/\omega) \\
+ a_0 (\dot{a_l}/\omega+b_l))+2/3 \lambda (\dot{a_l}/\omega)\\  
- (-\mu/3 a_0 + (.25-\epsilon/3) (\dot{a_l}/\omega+b_l)) \\ 
(-p/\omega sin(\beta_w)+q/\omega cos(\beta_w))\\ 
- (.25-\epsilon/3) (\dot{b_l}/\omega-a_l) (p/\omega cos(\beta_w)\\ 
+ q/\omega sin(\beta_w)) - .125 (-p/\omega sin(\beta_w)+q/\omega cos(\beta_w))^2 \\ 
-.125 (p/\omega cos(\beta_w)+q/\omega sin(\beta_w))^2 -  \\
(.25-2/3 \epsilon+\epsilon^2/2) ((\dot{a_0}/\omega)^2 \\ 
+ .5 ((\dot{a_l}/\omega+b_l)^2+(\dot{b_l}/\omega-a_l)^2))
\label{torquecoeff}
\end{multline}

Please see \cite{chen1979simplified} for definition of terms. Although this model takes into account all of the design variables chosen for this project, it is difficult to optimize because of the complexity of the functions. \textit{Currently, this model fails to converge to a solution, so we are working with it to find the source of the issue.}
